Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-21 paper.tex
intro cloud

>>>>

Nowadays, many cloud vendors have started offering virtual machines (VM) with GPUs in order to provide
GPGPU computation service to users who need it. An examples of that are:
Amazon Web Services (AWS), Penguin Computing, Softlayer and Microsoft Azure.
In the pubic scope, one of the most popular cloud vendors is AWS that has a wide range of preconfigured instances ready to be launched.
Otherwise, owning the propper infrastructure, a private cloud can be deployed using a specific middleware such as
Openstack or Opennebula.

However, in cloud environments sharing GPU resources among multiple VMs
is not straightforward as would be in a physical servers which is translated into a low utilization rate.
On the one hand, instances in public clouds are not customizable enough. 
On the other, in private cloud, although the instances can be customized in many aspects, when referring to GPUs
the number of options is reduced.
Moreover, neither vendors nor tools are offering GPGPU as a service and that is what we are pursing:
to offer flexibility and boost the utilization of GPU resources either in private or public clouds.
